---
title: "Triangle standard methods"
author: "Giulio Carnevale, Marco De Virgilis"
date: "3/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Create results

This document shows how to generate Chain Ladder and Standard Cape Cod results from the GISA data.    
It is assumed that the data itself has already been downloaded and processed with the script `generate_triangle_data.R`.  
The folder will contain the following files:    
  * `Alberta_Collision.xlsx`  
  * `Alberta_TPL_BI.xlsx`  
  * `Atlantic_Canada_Collision.xlsx`  
  * `Atlantic_Canada_TPL_BI.xlsx`  
  * `Nova_Scotia_Collision.xlsx`  
  * `Nova_Scotia_TPL_BI.xlsx`  
  * `Ontario_AB_DI.xlsx`  
  * `Ontario_AB_MR.xlsx`  
  * `Ontario_Collision.xlsx`  
  * `Ontario_TPL_BI.xlsx`  


The main script needed for the process is `generate_CL_CC_results.R` located in the `inst` folder. The next session will describe each step in the script file.

# generate_CL_CC_results.R

## Loading the required libraries

The libraries required for the analysis are:

```{r libraries}
library(gisadata) # can be installed with `remotes::install_github("kasaai/gisadata")`
library(readxl)
library(ChainLadder)
library(openxlsx)
library(tidyverse)

```

Let's suppose we have all the files processed in the `gisa_data` directory
```{r list}
dir_ls("gisa-data")
#> gisa-data/Alberta_Collision.xlsx  
#> gisa-data/Alberta_TPL_BI.xlsx  
#> gisa-data/Atlantic_Canada_Collision.xlsx
#> gisa-data/Atlantic_Canada_TPL_BI.xlsx 
#> gisa-data/Nova_Scotia_Collision.xlsx 
#> gisa-data/Nova_Scotia_TPL_BI.xlsx 
#> gisa-data/Ontario_AB_DI.xlsx
#> gisa-data/Ontario_AB_MR.xlsx
#> gisa-data/Ontario_Collision.xlsx  
#> gisa-data/Ontario_TPL_BI.xlsx          
```
Now it's possible to generate Chain Ladder and Cape Cod results by calling the functions `print_cl_results` and `print_cape_cod_results` on the name of the file (or the full path).  
Chain Ladder example:  
```{Chain Ladder results example}
print_cl_results("Alberta_Collision.xlsx")
print_cl_results("Alberta_TPL_BI.xlsx")
print_cl_results("Atlantic_Canada_Collision.xlsx")
print_cl_results("Atlantic_Canada_TPL_BI.xlsx")
print_cl_results("Nova_Scotia_Collision.xlsx")
print_cl_results("Nova_Scotia_TPL_BI.xlsx")
print_cl_results("Ontario_AB_DI.xlsx")
print_cl_results("Ontario_AB_MR.xlsx")
print_cl_results("Ontario_Collision.xlsx")
print_cl_results("Ontario_TPL_BI.xlsx")
```

Cape Cod example:  
```{Cape Cod results example}
print_cape_cod_results("Alberta_Collision.xlsx")
print_cape_cod_results("Alberta_TPL_BI.xlsx")
print_cape_cod_results("Atlantic_Canada_Collision.xlsx")
print_cape_cod_results("Atlantic_Canada_TPL_BI.xlsx")
print_cape_cod_results("Nova_Scotia_Collision.xlsx")
print_cape_cod_results("Nova_Scotia_TPL_BI.xlsx")
print_cape_cod_results("Ontario_AB_DI.xlsx")
print_cape_cod_results("Ontario_AB_MR.xlsx")
print_cape_cod_results("Ontario_Collision.xlsx")
print_cape_cod_results("Ontario_TPL_BI.xlsx")      
```

These two functions produce the results appending in the name of the file the name of the method.  
The final folder will contain the following files:  

```{final folder}
dir_ls("gisa-data")
#> Alberta_Collision_Chain_Ladder.xlsx
#> Alberta_TPL_BI_Chain_Ladder.xlsx
#> Atlantic_Canada_Collision_Chain_Ladder.xlsx
#> Atlantic_Canada_TPL_BI_Chain_Ladder.xlsx
#> Nova_Scotia_Collision_Chain_Ladder.xlsx
#> Nova_Scotia_TPL_BI_Chain_Ladder.xlsx
#> Ontario_AB_DI_Chain_Ladder.xlsx
#> Ontario_AB_MR_Chain_Ladder.xlsx
#> Ontario_Collision_Chain_Ladder.xlsx
#> Ontario_TPL_BI_Chain_Ladder.xlsx
#> Alberta_Collision_Cape_Cod.xlsx
#> Alberta_TPL_BI_Cape_Cod.xlsx
#> Atlantic_Canada_Collision_Cape_Cod.xlsx
#> Atlantic_Canada_TPL_BI_Cape_Cod.xlsx
#> Nova_Scotia_Collision_Cape_Cod.xlsx
#> Nova_Scotia_TPL_BI_Cape_Cod.xlsx
#> Ontario_AB_DI_Cape_Cod.xlsx
#> Ontario_AB_MR_Cape_Cod.xlsx
#> Ontario_Collision_Cape_Cod.xlsx
#> Ontario_TPL_BI_Cape_Cod.xlsx
```

Each file contains the results for the specified method for both Incurred and Paid data.
