---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gisadata

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/kasaai/gisadata.svg?branch=master)](https://travis-ci.org/kasaai/gisadata)
[![Codecov test coverage](https://codecov.io/gh/kasaai/gisadata/branch/master/graph/badge.svg)](https://codecov.io/gh/kasaai/gisadata?branch=master)
<!-- badges: end -->

Workflow functions for tidying up claims data from the General Insurance Statistical
Agency (GISA) of Canada.

## Installation

```r
remotes::install_github("kasaai/gisadata")
```

## Example

Attach necessary packages:

```{r example, message=FALSE}
library(gisadata)
library(tidyverse)
library(fs)
```

Suppose the data archives are in the `gisa-data` directory:

```{r}
dir_ls("gisa-data")
```

We can extract the CSV files by calling `gisa_unzip()`:

```{r}
# By default, files are extracted to a temp directory
extract_dir <- gisa_unzip("gisa-data")
dir_ls(extract_dir)
```

Read and process tables:

```{r}
data_auto <- extract_dir %>% 
  path("Auto Loss Development") %>% 
  gisa_process_auto_dev()

data_auto$`Loss development exhibit - Private Passenger - All Perils - AB` %>% 
  glimpse()
```

## Contributing

- Do not commit any (real) data files.
- Follow [Tidyverse style guide](https://style.tidyverse.org/).
