---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gisadata

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/kasaai/gisadata.svg?branch=master)](https://travis-ci.org/kasaai/gisadata)
[![Codecov test coverage](https://codecov.io/gh/kasaai/gisadata/branch/master/graph/badge.svg)](https://codecov.io/gh/kasaai/gisadata?branch=master)
<!-- badges: end -->

Workflow functions for tidying up claims data from the General Insurance Statistical
Agency (GISA) of Canada.

## Installation

```r
remotes::install_github("kasaai/gisadata")
```

## Example

Attach necessary packages:

```{r example, message=FALSE}
library(gisadata)
library(tidyverse)
library(fs)
```

Suppose the data archives are in the `gisa-data` directory:

```{r}
dir_ls("gisa-data")
```

We can extract the CSV files by calling `gisa_unzip()`:

```{r}
# By default, files are extracted to a temp directory
extract_dir <- gisa_unzip("gisa-data")
extract_dir
```

The necessary metadata for ingesting the files can be obtained from `gisa_col_specs()`
and `gisa_headers()`.

```{r}
col_specs <- gisa_col_specs()
headers <- gisa_headers()
headers$liability %>% head()
```

Read and process tables:

```{r}
data_liab <- extract_dir %>%
  path("CLSP") %>%
  dir_ls() %>%
  map(read_csv,
          col_names = headers$liability,
          col_types = col_specs$liability) %>%
  imap(~ .x %>%
         gisa_rename_cols() %>%
         mutate(file = str_extract(.y, "LIAB\\d{4}")) %>%
         left_join(gisa_exhibit_mapping(), by = c("file", "section_number"))) %>%
  map(~ group_split(.x, exhibit)) %>%
  flatten() %>%
  set_names(map_chr(., ~ first(.x$exhibit))) %>%
  map(~ .x %>% 
        gisa_select_cols(first(.x$format_number)) %>% 
        gisa_liab_map_levels())

data_liab$`Loss Development - CGL - with product/completed operations` %>% 
  glimpse()
```

## Contributing

- Do not commit any (real) data files.
- Follow [Tidyverse style guide](https://style.tidyverse.org/).
- Column renaming uses the mapping table under [`data-raw`](https://github.com/kasaai/gisadata/tree/master/data-raw). 
If you're making a change, the accompanying script should be run and the 
resulting `R/sysdata.rda` committed.
- Column headers are kept in [`inst/extdata`](https://github.com/kasaai/gisadata/tree/master/inst/extdata).
- Sample uncompressed files are kept in [`inst/testdata/gisa-data`](https://github.com/kasaai/gisadata/tree/master/inst/testdata/gisa-data).
- Input types of each type of table are explicitly specified in [`R/col-specs.R`](https://github.com/kasaai/gisadata/blob/master/R/col-specs.R).
